---
title: "WindmillEfficiency"
author: "Charlie Wilson, Russell Fager, Tommy King"
date: "3/8/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
library(ggpubr)
```
Test function to see if it works:

Using windmill_power function, compute windmill power output for 4 different scenarios assuming baseline windspeed of 50 m/s:
* Windmill A  swept area 25m^2, generator efficiency 0.2

* Windmill B swept area 50m^2, generator efficiency 0.3

* Windmill C swept area 75m^2, generator efficiency 0.4

* Windmill D swept area 100m^2, generator efficiency 0.5

Mean wind velocity = 25 m/s 

```{r}
source("R/windmill_power.R")
# generate a structure to store info on our possible wind outputs
possible_turbines = data.frame(name = c("A","B","C", "D"),swept_area=c(25,50,75,100), generator_eff = c(0.2,0.3,0.4,0.5))

speed_base = 25
# estimate power for each scenario
# add to the data structure
possible_turbines$power = windmill_power(V=speed_base, Ng=possible_turbines$generator_eff, A = possible_turbines$swept_area)
#head(possible_turbines)
# show results                         
ggplot(possible_turbines, aes(x=swept_area, y=power, fill=as.factor(swept_area)))+geom_col()+labs(y="Power (Watts)", x="Swept Area (m2)", fill="Swept Area (m2)")
possible_turbines

```
```{r}
source("R/windmill_power.R")

#We created a windmill power function with several inputs and parameters the generates two outputs wind power in kWh and revenue from wind power based on current market price (12 cents)

windmill_power(A= 25, V = 40, Ng = .3)
```




```{r withforloop}
#using for loop
# use sample to generate a distribution of wind velocities 
# assume a log normal distribution of wind speeds with mean 25 m/s
# assume standard deviation of 5%
nsample = 200
sweptareas = rnorm(mean=50, sd=15, n=nsample)
summary(sweptareas)
plot(density(sweptareas), ylab="Distribution of swept areas in (m^2)")

# use a for loop to cycle through each scenario
# create a data frame to store results 
# one column for each turbine and one row for each speed
wind_speeds = data.frame(name = c("20mps","15mps","10mps","5mps"),V=c(20,15,10,5))


allSweptAreaspower = data.frame(matrix(nrow=length(sweptareas),ncol = length(wind_speeds$name)))


# Create power outputs using nested for loop
for(i in 1:length(wind_speeds$V)){
  for(j in 1:nsample){
    allSweptAreaspower[j,i]=windmill_power(V = wind_speeds$V[i],A = sweptareas[j], hidePower = FALSE, hidePrice = TRUE)
  }
}

colnames(allSweptAreaspower) = wind_speeds$name

#make usable for boxplot
allSweptAreaspower2 = allSweptAreaspower %>% pivot_longer(cols=everything(), names_to="WindSpeed", values_to="Power")

#Create data frame for revenue
allSweptAreasprice = data.frame(matrix(nrow=length(sweptareas),ncol = length(wind_speeds$name)))



# Create power outputs using nested for loop
for(i in 1:length(wind_speeds$V)){
  for(j in 1:nsample){
    allSweptAreasprice[j,i]=windmill_power(V = wind_speeds$V[i],A = sweptareas[j], hidePower = TRUE, hidePrice = FALSE)
  }
}

colnames(allSweptAreasprice) = wind_speeds$name

allSweptAreasprice2 = allSweptAreasprice %>% pivot_longer(cols=everything(), names_to="WindSpeed", values_to="Price")


sweepAreaPurpower = pmap(list(V = wind_speeds$V), windmill_power, A=sweptareas, hidePower = FALSE, hidePrice = TRUE)

# covert to usible data frame for boxplot
sweepAreaPurpower = as.data.frame(sweepAreaPurpower, col.names=wind_speeds$name)

# assign x and y values to dataframe to help create a boxplot
sweepAreaPurpower2 = sweepAreaPurpower %>% pivot_longer(cols=everything(), names_to="WindSpeed", values_to="power")

#Pur method for Price
sweepAreaPurPrice = pmap(list(V = wind_speeds$V), windmill_power, A=sweptareas, hidePower = TRUE, hidePrice = FALSE)

# covert to usible data frame for boxplot
sweepAreaPurPrice = as.data.frame(sweepAreaPurPrice, col.names=wind_speeds$name)

# assign x and y values to dataframe to help create a boxplot
sweepAreaPurPrice2 = sweepAreaPurPrice %>% pivot_longer(cols=everything(), names_to="WindSpeed", values_to="price")

```


# Boxplots

```{r}

#boxplot for power
ggplot(allSweptAreaspower2, aes(WindSpeed,Power,fill=WindSpeed))+geom_boxplot()+ggtitle("Windmill Power Output") + labs( y = "Power (kWh)")

#Boxplot for price
ggplot(allSweptAreasprice2, aes(WindSpeed,Price,fill=WindSpeed))+geom_boxplot()+ggtitle("Windmill Revenue") + labs( y = "$ per second")
```

